---
title: "Chapter 3: Basic Statistics: A Review"
author: "Mimi Wang"
date: "12/2/2019"
output:
  github_document:
    pandoc_args: --webtex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(latex2exp)
```

### Problem 14

From two normal populations assumed to have the same variance, independent random samples of sizes 15 and 19 were drawn.  The first sample (with $n_1 = 15$) yielded mean and standard deviation 111.6 and 9.5, respectively, while the second sample ($n_2 = 19$) gave mean and standard deviation 100.9 and 11.5, respectively.  The estimated standard error of the difference in sample means is _______.

The equation for pooled variance:
$$S_p^2 = \frac{(n_1 - 1)S_1^2 + (n_2 - 1)S_2^2}{n_1 + n_2 - 2}$$

The equation for standard error:
$$SE = S_p \sqrt{\frac{1}{n_1} + \frac{1}{n_2}}$$

```{r}
# First, calculate the pooled sample variance
var_pooled <- ((15 - 1) * 9.5^2 + (19 - 1) * 11.5^2) / (15 + 19 - 2)

# Then calculate the standard error
se <- sqrt(var_pooled) * sqrt(1 / 15 + 1 / 19)
se
```


