---
title: "Chapter 3: Basic Statistics: A Review"
author: "Mimi Wang"
date: "12/2/2019"
output:
  github_document:
    pandoc_args: --webtex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(latex2exp)
```

### Problem 16

Test the null hypothesis that the true population average body weight is the same for two independent diagnosis groups from one hospital versus the alternative hypothesis that these two population averages are different, using the following data:

Diagnosis group 1 data: [132, 145, 124, 122, 165, 144, 151]

Diagnosis group 2 data: [141, 139, 172, 131, 150, 125]

You may assume that the populations from which the data come are each normally distributed, with equal population variances.  What conclusion should be drawn, with $\alpha = .05$?

```{r}
# Get T score
data_1 <- c(132, 145, 124, 122, 165, 144, 151)
data_2 <- c(141, 139, 172, 131, 150, 125)

var_pooled <- (length(data_1) - 1) * var(data_1) + (length(data_2) - 1) * var(data_2)
var_pooled <- var_pooled / (length(data_1) + length(data_2) - 2)

T <- (mean(data_1) - mean(data_2)) / (sqrt(var_pooled) * sqrt((1 / length(data_1)) + (1 / length(data_2))))
abs(T)
```

```{r}
# Get T Score
qt(0.975, df = length(data_1) + length(data_2) - 1)
```

2.18 > 0.289, so we do not reject the null hypothesis.